---
title: "p8105_hw1_zl3804.Rmd"
author: "eva/Zhuoxuan Li"
date: "2026-09-22"
output: github_document
---
# Section 0 
```{r}
library(tidyverse)
```

# Section 1 download dataset from package
```{r}
 data("penguins", package = "palmerpenguins")
```
This datasheet contains `r nrow(penguins)` subjects and `r ncol(penguins)` variables to describe the dimensions of penguins, introducing us the year, species, island, sex of those penguins, and bill_length_mm, bill_depth_mm, flippers_length_mm, body_mass_g in relative measures.
Among those, mean of their flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`mm.

# Section 2 Make a  scatterplot
```{r}
ggplot(penguins, aes(x= bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatterplot.png")

```

# Section 3 Create dataframe

```{r}
library(tidyverse)

set.seed(8130)

frame_samp = tibble(
  normx = rnorm (10),
  log_normx = normx > 0,
  character = c ("y", "o", "c", "o", "m", "p", "r", "o", "u", "n"),
  level = factor(sample(c("high", "medium", "low"), 10, replace = TRUE))
)  

mean_normx = mean(pull(frame_samp, normx))
mean_log_normx = mean(pull(frame_samp, log_normx))
mean_chara = mean(pull(frame_samp, character))
mean_level = mean(pull(frame_samp, level))

```
Show which variable can caculate means and which can't :
The mean of normal distribution R.V. is `r mean_norm`
The mean of logic function outcoe is  `r mean_log_normx`
The mean of characters is `r mean_chara`
The mean of factor R.V. is `r mean_level`



  



 

