---
title: "p8105_hw1_zl3804.Rmd"
author: "Eva/Zhuoxuan Li"

date: "2026-09-22"
output: github_document
---
# Section 0 
```{r}
library(tidyverse)
```

# Section 1 download dataset from package
```{r}
 data("penguins", package = "palmerpenguins")
```
This datasheet contains `r nrow(penguins)` subjects and `r ncol(penguins)` variables to describe the dimensions of penguins, introducing us the year, species, island, sex of those penguins, and bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g in relative measures.
Among those, mean of their flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)`mm.

# Section 2 Make a  scatterplot
```{r}
ggplot(penguins, aes(x= bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatterplot.png")

```

# Section 3 Create dataframe

```{r}
library(tidyverse)

set.seed(8130)

frame_samp = tibble(
  normx = rnorm (10),
  log_normx = normx > 0,
  character = c ("y", "o", "c", "o", "m", "p", "r", "o", "u", "n"),
  level = factor(sample(c("high", "medium", "low"), 10, replace = TRUE))
)  

mean_normx = mean(pull(frame_samp, normx))
mean_log_normx = mean(pull(frame_samp, log_normx))
mean_chara = mean(pull(frame_samp, character))
mean_level = mean(pull(frame_samp, level))

```
Show which variable can caculate means and which can't :

The mean of normal distribution R.V. is `r mean_normx`

The mean of logic function outcome is  `r mean_log_normx`

character and level can't get means because the results are 'NA'

# Section 4 Convert variable types

```{r echo = TRUE, results='hide'}
convert_log = as.numeric(pull(frame_samp,log_normx))
convert_chara = as.numeric(pull(frame_samp, character))
convert_fac = as.numeric(pull(frame_samp, level))

```

We can see when we do coercion, the warning said NAs are created:

logic type turned into `r convert_log`, which are meaning numbers.

But characters showed up as NA, which aligns with the outcome that characters can't get a mean.

For factor type variable , although level can become numbers `r convert_fac`after convertion, computers ban factor variables to calculate means in order to prevent misunderstanding of mean of categories.



  



 

